In this section, you will describe all of the various artifacts that you will generate and maintain during the project lifecycle. Describe the purpose of each item below, how the content will be generated, where it will be stored, how often it will be updated, etc. 

\subsection{Project Charter}
The charter shall remain online for all team members to update, and will be audited by the site's History and Revisions section. The charter shall be updated as needed for the benefit of project clarity as the project approaches completion.

\subsection{Product Backlog}
A backlog shall be maintained using the Trello App, a plugin through the group's slack website. The team shall
list urgency of backlogged tasks in descending order.

\subsection{Sprint Planning}
Sprint planning sessions shall be held after every other scrum, decisions shall be made by a group vote, ties will be resolved either by random chance, or council with a third party.

\subsubsection{Sprint Goal}
Sprint goals shall be determined by team vote.

\subsubsection{Sprint Backlog}
The sprint backlog will be determined by the current scrum master, and will be descending order of urgency.

\subsubsection{Task Breakdown}
Tasks will first be assigned by volunteer, then by assessment of skills, or failing that, random chance.

\subsection{Sprint Burndown Charts}
The standing scrum master will construct the sprint burndown chart for the current sprint.

\subsection{Sprint Retrospective}
Sprint retrospectives will be held immediately before the next sprint.

\subsection{Individual Status Reports}
Status reports will be given each meeting, important information should be presented at the start of the meeting.

\subsection{Engineering Notebooks}
Every team member will maintain their own notebook, and will be signed by fellow team members.

\subsection{Closeout Materials}
No physical material will be shipped out, as it is a software application.

\subsubsection{System Prototype}
The prototype system will only have computer vision functionality, later prototypes may have UI and social media functionality.

\subsubsection{Project Poster}
The team shall design a poster to display the difference between out product and those mentioned in related work.

\subsubsection{Web Page}
We will make a simple webpage with instructions on how to use the app, the app may contain a link to the website, and the website may have a download link for the app.

\subsubsection{Demo Video}
A demo video may be made and imbedded into the website.

\subsubsection{Source Code}
The source code will be kept in google docs for the team to access, and the source code will be evaluated at the end of the project, and be made open source or kept private depending on factors made in development.

\subsubsection{Source Code Documentation}
The source code will be documented as modules are installed to the system.

\subsubsection{Hardware Schematics}
There are no hardware components required for this project, no schematics will be designed.

\subsubsection{CAD files}
There are no physical components requiring CAD files, no CAD files will be designed.

\subsubsection{Installation Scripts}
The scripts for installation will be made to work with an app store or by website download.

\subsubsection{User Manual}
Instructions for use may be included on the website, and will consist of a few paragraphs of instructions.